### 2016-03-04 documentation/EnTrI/EnTrI.tex
Fixed a bug in insertion-position-bias.py

The bias towards the position of insertions within genes has been studied since the genes can tolerate lower number of insertions at the start of the gene. We have divided our genes into 3 parts: first 60 nucleotides, last 60 nucleotides, and the rest and plotted the normalised number of insertions in each of these groups. Figure~\ref{fig:insertion-position-bias} summarises the results.

>>>>

The bias towards the position of insertions within genes has been studied since the genes can tolerate more insertions at the 3' end of the gene. We have divided our genes into 3 parts: first 60 nucleotides, last 60 nucleotides, and the rest and plotted the normalised number of insertions in each of these groups. Figure~\ref{fig:insertion-position-bias} summarises the results.
